Hydras \& Co.

### 2023-11-23 doc/chapter-primrec.tex
minor corrections

@@

@@

\begin{remark}
Note that the Ackermann function is a counter-example to the (false) statement:
\begin{quote}
{\color{red}
  ``Let $f$ be a function of type \texttt{naryFunc\,2}. If, for any $n$, the function $f(n)$ is primitive recursive, then f is primitive recursive.''}
\end{quote}
\end{remark}

>>>>

\label{sect:AcknPR}

@@

\begin{todo}
Fix the display the local definition of \texttt{x} in the following proof.
\end{todo}

@@

\begin{remark}
  It may be interesting to compare the following statements:

  \begin{itemize}
  \item Ackermann function is not primitive recursive.
  \item For any $n$, the function \texttt{Ack $n$ \_} is primitive recursive (see~\vref{sect:AcknPR}).
  \end{itemize}
\end{remark}
